Theory about Normal Basis on $F(2^k)$

### 2016-12-24 dissertation/submission/conclude.tex
dissertation after defense update 2

Consider Buchberger's algorithm, all generators' leading terms are relatively prime, so it is a GB itself. 
Then we need to reduce this GB, we will find out $S + \mathcal G(x)$ could (possibly) be reduced by $v_x$,
and $T+\mathcal F(S,x)$ will definitely reduced by $S + \mathcal G(x)$. So, at last we will get a polynomial
$T + \mathcal F'(x)$ in reduce GB. We can include this polynomial and $v_x$, exclude the polynomial containing
$S$ (i.e. $\mathcal H(S)$ in algorithm), to compose an ideal representing \emph{next states} $to^i$. 
In iteration 1, result is $to^1 = \langle T+1, x^2+x\rangle$

@@

\begin{figure}[h]
\centerline{
\includegraphics[width=0.35\textwidth]{newfig/ZDD.eps}
}
\caption{A ZDD representing remainder polynomial reducing by a chain of OR gates with order $d>c>b>a$}
\label{fig:ZDD}
\end{figure}

@@

\begin{figure}[h]
\centering{
\includegraphics[width=4.5in]{newfig/project.eps}
\caption{Algebraic interpolant: Projection of varieties on common variables }
\label{fig:projection}}
\end{figure}

@@

\subsection{Technology Mapping for Word-level Functional Blocks}
Technology mapping is an important problem in digital circuit synthesis.
Designers are given a library of well-designed functional/macro blocks (including IP cores) and a raw netlist, 
technology mapping's objective is to map as many as blocks to the raw netlist and 
keep the functional equivalence. Contemporary techniques rely on bit-wise 
analysis on the signals to deduce the boundary of mapped blocks.
It is possible to use the equivalence checking techniques proposed in this dissertation 
as a alternative way to perform technology mapping, especially on word-level when 
given blocks represent word-level functions.

\begin{Problem}
The objective of our approach is to map the macro blocks without boundary information.
Mapping is an essential technique used in synthesis and verification. In synthesis, we can map the 
macro functions with smaller and faster implementations to optimize the timing and area; in simulation,
we can map a complicated function to a simple execution to accelerate simulation speed.

Given a gate-level design $D$ and several word-level macro blocks $\{B_i\}$, we need to map macro
blocks $B_i$ into design $D$, and write out the mapped design $D'$ which is equivalent to original
design $D$. The objective is to generate a mapped design $D$ with as many of $B_i$ such that the area
and timing is optimal. The procedure is also illustrated in Figure \ref{fig:macro}.

\begin{figure}[h]
	\begin{center}
	\includegraphics[width=\textwidth]{newfig/macro.pdf}
	\end{center}
	\caption{The outline and flow of technology mapping of macro blocks}
	\label{fig:macro}
\end{figure}

@@

1) {\bf Template and state constraints:}  Ideal membership test technique requires a setup of ideal $J_{loop}$
for loop invariants. 
One heuristic can provide better coverage for loop invariant abstraction as well as
relatively small size is \emph{generic quadratic form} (GQF).

For example, the GQF of a pair of state variables $\{x,y\}$ is
$$\Func = a_0x^2+a_1x+a_2xy+a_3y+a_4y^2+a_5$$
It covers all possible terms with degree no more than 2. $a_0,a_1,\dots, a_5$ are usually real number parameters,
some of their assignments can turn $\Func$ into desired invariant. This parameterized constrain
polynomial covers all combinations of state variables can also be called a \emph{template}.
Subsequently, finding a proper assignment is the essential part of in our proposed research.

2) {\bf Initial state constraints:} For initial states, the constrains are explicit. A template is adopted and refined by Gr\"obner basis 
generated by original constrains, by equaling the remainder to 0 we can get constrains on
parameters from the template.

@@

Its template is generic quadratic form of $\{s,i,j,j_0\}$, which is
\begin{align}
\Func = & a_0s^2+a_1s+a_2si+a_3sj+a_4sj_0\nonumber\\
&a_5i^2+a_6i+a_7ij+a_8ij_0+a_9j^2\nonumber\\
&a_{10}j+a_{11}jj_0+a_{12}j_0^2+a_{13}j_0+a_{14}\nonumber
\end{align}
with parameters $a_0,\dots,a_{14}$.

Constrains of initial state $s=0\land j=j_0$ can be interpreted to polynomials:
$$\{s, j-j_0\}$$
Since their leading terms are relatively prime, the polynomial set itself constitutes a Gr\"obner basis 
$$G=\{s, j-j_0\}$$ 
Therefore its ideal can be written as
$J=\langle s,j-j_0\rangle$.

In the next step, we reduce the template with the Gr\"obner basis $G$: $\Func \xrightarrow{G}_+ r$, the remainder equals to
$$r = a_5i^2+a_6i+(a_7+a_8)ij_0+(a_9+a_{11}+a_{12})j_0^2+(a_{10}+a_{13})j_0+a_{14}$$
Let it equal to 0, then each coefficient will generate a constraint. The solution to the system forms the candidate
assignment to generate loop invariants.
\begin{equation}
\left\{
\begin{array}{l}
a_5=a_6=a_{14}=0\\
a_7+a_8=0\\
a_9+a_{11}+a_{12}=0\\
a_{10}+a_{13}=0
\end{array}\right.
\nonumber
\end{equation}

3) {\bf Modeling state transitions:}
A typical state transition starts from the previous state (PS) and ends at next state (NS). 
Our proposed approach models the 2 states individually,
{i.e.} performs polynomial reduction separately and obtains remainder $r_1$ and $r_2$. 
Assume a constraint polynomial describing
the state transition is $r_t$, then we require that when invariant of PS holds and transition $PS \to NS$ stands,
invariant of NS should also be satisfied:
$$(r_1 = 0)\land (r_t = 0) \implies (r_2 = 0)$$
One reasonable conjecture is
$$r_t = r_1 - \lambda r_2$$
Theoretically $\lambda$ can be any polynomial in arbitrary rings. To make it practical solving the system, 
we limit $\lambda$ to the polynomial ring with only real numbers.

We take Equation \ref{eqn:loopinv} as the example (which refers to Example 10 in \cite{sankaranarayanan2004non}). 
PS is initial state we just characterized 
$$\Func = f(s,i,j,j_0)$$ 
and NS has exactly the same form of constraint:
$$\Func' = f(s',i',j',j_0')$$
Considering the transition relation, we substitute $s'$ with $s+i$ and replace $j'$
with $j-1$, $i'$ for $i$, $j_0'$ for $j_0$, respectively. 
The template for NS is polynomial $f'$ in Example 10 in \cite{sankaranarayanan2004non}.

We then perform reduction with the Gr\"obner basis generated from the transition relation modeling, 
and record its remainder $r_2$.
From equality $r_2 = \lambda r_1$, we get constraints for the parameters. Solve the system using 
similar algorithm to solve binate covering problems
which is also described in Section 4 as \emph{elimination by splitting} technique in \cite{sankaranarayanan2004non}. 
One branching result is:
\begin{align*}
&a_0,a_2,\dots, a_6, a_9,\dots,a_{14}=  0\\ 
&a_1=a_7=-a_8
\end{align*}
The reduced remainder is: 
$$r_2 = a_1s +(a_1-a_7)i+a_7ij+a_8ij_0 = a_1(s+ij-ij_0) = 0$$
Thus the invariant of the program in Equation \ref{eqn:loopinv} is:
$$s = i(j_0- j)$$
We can verify the invariant by executing the program which calculates $i\times j_0$. 
Initially $s=0$, $j_0-j=0$, invariant holds;
during each cycle, $s'=s+i, (j_0'-j') = (j_0-j)+1$, the invariant also holds. In conclusion, this is a
loop invariant for program in Equation \ref{eqn:loopinv}.

{\bf Our proposed approach on technology mapping:}
Our approach borrows inspiration of templates in \cite{sankaranarayanan2004non}. However, we make an improvement
on the original approach:
instead of using template polynomial to describe the system, we add some templates into the ideal
of macro blocks which serve as technology mapping candidates. In this way we can cover all possibilities
of boundary cutting (circuit partition).

1) {\bf System abstraction:}
The polynomial we use to test ideal membership should include all information of a circuit partition,
which requires us to abstract information from the system and write it into a single polynomial.
Usually this polynomial has the following generic form:
$$Z + f(i_1,i_2,\dots,i_n)$$
where $Z$ is the output. When there is only one output, $Z$ collapse to a bit-level variable. However in most
cases there are multiple outputs on the cut, indicating $Z$ as a word-level variable. Boolean function $\Func$ covers
all inputs, and $i_1,i_2,\dots,i_n$ are all bit-level inputs.

\begin{figure}[h]
	\begin{center}
	\includegraphics[width=\textwidth]{newfig/tobemapped.pdf}
	\end{center}
	\caption{An example gate-level netlist to be mapped}
	\label{fig:tobemapped}
\end{figure}

Figure \ref{fig:tobemapped} shows an example circuit partition with $a_1,b_1,a_0,b_0$ as inputs and
$Z = \{z_0,z_1\}$ as outputs. If we use elements from Galois field $\F_{2^2}$ to represent word $Z$,
we have $Z = z_0 + \alpha\cdot z_1$.

After imposing ATO of LEX with
$$Other\ circuit\ variables > output\ word\ Z > all\ bit\ level\ inputs$$
on the ideal describing the partitioned circuit as well as ideal with vanishing polynomials,
the reduced Gr\"obner basis has a single polynomial generator in the form of $Z + \Func(a_1,b_1,a_0,b_0)$.
In this example:

\begin{itemize}
\item Term ordering: $\{z_0,z_1,t,g_1,p_1,ci,t_1,t_2\}>Z>\{a_0,b_0,a_1,b_1$
\item Gate description: $z_0+t+g_1+t\cdot g_1, t+t_1+t_2+t_1\cdot t_2, g_1+a_1\cdot b_1,
			t_1+a_1\cdot ci, t_2+b_1\cdot ci, ci+a_0\cdot b_0, z_1+p_1+ci, p_1+a_1+b_1$
\item Word definition: $Z+z_0+z_1\cdot \alpha$
\item Vanishing polynomial ideal $(J_0)$: $z_0^2+z_0, z_1^2+z_1, t^2+t, g_1^2+g_1, t_1^2+t_1, t_2^2+t_2, p_1^2+p_1, ci^2+ci,
			a_0^2+a_0, b_0^2+b_0, a_1^2+a_1, b_1^2+b_1, Z^4+Z$(since Z is a 2-bit word)
\end{itemize}

The result is a Gr\"obner basis with single polynomial generator. The polynomial has leading term $Z$:
$$Z+a_0\cdot b_0\cdot a_1+a_0\cdot b_0\cdot b_1+\alpha\cdot a_0\cdot b_0+a_1\cdot b_1+\alpha\cdot a_1+\alpha\cdot b_1$$

@@

2) {\bf Templates on Boundary Information:}
\begin{figure}[h]
	\begin{center}
	\includegraphics[width=\textwidth]{newfig/template.pdf}
	\end{center}
	\caption{Standard 2-bit adder with input/output mapping}
	\label{fig:template}
\end{figure}

Figure \ref{fig:template} shows a 2-bit standard cell. It has 3 outputs mapped to 2 output pins,
and 4 inputs mapped to 3 input pins (the rest pins are assigned to fixed 0/1 signal). Dashed connection
lines show one possible mapping, to find out this kind of feasible mapping, we need to simulate
all possible mappings, where the concept "template" can be used.

{\it Output template}: $z_0+c_{{t_0}{z_0}}\cdot t_0+c_{t_1z_0}\cdot t_1+c0_{CO}\cdot CO+c_{n_0}$

When $c_{n_0} = 0$, then $\{c_{t_0z_0},c_{t_1z_0},c0_{CO}\}$ equals to 1 denotes a valid mapping to corresponding output pin. 
Conversely if $cn0 = 1$, the ``1" evaluation denotes mapping to negation of corresponding output pin.

{\it Input template}: $a_0+p_{a_0}+c0_{A_0}\cdot s_0+c1_{A_0}\cdot s_1+c2_{A_0}\cdot s_2$

When $p_{a_0} = 0$, then $\{c0_{A_0},c1_{A_0},c2_{A_0}\}$ equal to 1 denotes a valid mapping to corresponding input
pin. Conversely if every variable in set $\{c0_{A_0},c1_{A_0},c2_{A_0}\}$ equals to 0, it denotes mapping to fixed signal ``0" (when $p_{a_0} = 1$ then
mapping to fixed signal ``1").

With these settings, we propose an approach to perform technology mapping with boundary information:
\begin{itemize}
\item First, choose a set of independent wires as input pins;

\item Second, push forward input signal for a certain number of gates (depth), choose a cut set
which fully dependent on these inputs as output pins;

\item Third, abstract a description polynomial using GB based abstraction;

\item Fourth, reduce the description polynomial with the GB we computed associated to macro block 
and templates, obtain a remainder polynomial;

\item Last but not least, abstract all coefficients from the remainder polynomial and set up a system of equations.
If we find a solution to this system, then the solution is a feasible mapping; no solution means we cannot make a
feasible mapping.
\end{itemize}

>>>>

Consider Buchberger's algorithm, all generators' leading terms are relatively prime, so it is a GB itself. 
Then we need to reduce this GB, we will find out $S + \mathcal G(x)$ could (possibly) be reduced by $v_x$,
and $T+\mathcal F(S,x)$ will definitely reduced by $S + \mathcal G(x)$. So, at last we will get a polynomial
$T + \mathcal F'(x)$ in reduce GB. We can include this polynomial and $v_x$, exclude the polynomial containing
$S$ ({\it i.e.} $\mathcal H(S)$ in algorithm), to compose an ideal representing \emph{next states} $to^i$. 
In iteration 1, result is $to^1 = \langle T+1, x^2+x\rangle$

@@

\begin{figure}[h]
\centerline{
\includegraphics[width=0.35\textwidth]{newfig/ZDD.eps}
}
\caption{A ZDD representing remainder polynomial reducing by a chain of OR gates with order $d>c>b>a$.}
\label{fig:ZDD}
\end{figure}

@@

\begin{figure}[h]
\centering{
\includegraphics[width=4.5in]{newfig/project.eps}
\caption{Algebraic interpolant: projection of varieties on common variables.}
\label{fig:projection}}
\end{figure}

@@

\subsection{Technology Mapping for Word-Level Functional Blocks}
Technology mapping is an important problem in digital circuit synthesis.
Designers are given a library of well-designed functional/macro blocks (including IP cores) and a raw netlist.
Technology mapping's objective is to map as many as blocks to the raw netlist and 
keep the functional equivalence. Contemporary techniques rely on bit-wise 
analysis on the signals to deduce the boundary of mapped blocks.
It is possible to use the equivalence checking techniques proposed in this dissertation 
as a alternative way to perform technology mapping, especially on word-level when 
given blocks represent word-level functions.

The objective of our approach is to map the macro blocks without boundary information.
Mapping is an essential technique used in synthesis and verification. In synthesis, we can map the 
macro functions with smaller and faster implementations to optimize the timing and area; in simulation,
we can map a complicated function to a simple execution to accelerate simulation speed.

\begin{Problem}
Given a gate-level design $N$ and several word-level macro blocks $\{B_i\}$, we need to map macro
blocks $B_i$ into design $N$, and write out the mapped design $N'$ which is equivalent to original
design $D$. The objective is to generate a mapped design $N'$ with as many of $B_i$ such that the area
and timing is optimal. The procedure is also illustrated in Figure \ref{fig:macro}.

\begin{figure}[h]
	\begin{center}
	\includegraphics[width=\textwidth]{newfig/macro.pdf}
	\end{center}
	\caption{The outline and flow of technology mapping of macro blocks.}
	\label{fig:macro}
\end{figure}

@@

1) {\bf Template and state constraints:}  Ideal membership test requires a setup of ideal $J_{loop}$
for loop invariants. 
One heuristic that can provide better coverage for loop invariant abstraction as well as a
relatively small size is \emph{generic quadratic form} (GQF).

For example, the GQF of a pair of state variables $\{x,y\}$ is
$$\Func = a_0x^2+a_1x+a_2xy+a_3y+a_4y^2+a_5$$
It covers all possible terms with degree no more than 2. Constants $a_0,a_1,\dots, a_5$ are 
usually real number parameters,
some of their assignments can turn $\Func$ into the desired invariant. This parameterized constraint
polynomial covers all combinations of state variables, and is also called a \emph{template}.
Subsequently, finding a proper assignment is the essential part of our proposed research.

2) {\bf Initial state constraints:} For initial states, the constraints are explicit. 
A template is adopted and refined by the Gr\"obner basis 
generated by original constraints, by equaling the remainder to 0 we can get constraints on
parameters from the template.

@@

Its template is the generic quadratic form of $\{s,i,j,j_0\}$, which is
\begin{align}
\Func &= a_0s^2+a_1s+a_2si+a_3sj+a_4sj_0\nonumber\\
&+a_5i^2+a_6i+a_7ij+a_8ij_0+a_9j^2\nonumber\\
&+a_{10}j+a_{11}jj_0+a_{12}j_0^2+a_{13}j_0+a_{14}\nonumber
\end{align}
with parameters $a_0,\dots,a_{14}$.

Constraints of initial state $s=0\land j=j_0$ can be interpreted as polynomials:
$$\{s, j-j_0\}$$
Since their leading terms are relatively prime, the polynomial set itself constitutes a Gr\"obner basis 
$$G=\{s, j-j_0\}$$ 
Therefore its ideal can be written as
$J=\langle s,j-j_0\rangle$.

In the next step, we reduce the template with the Gr\"obner basis $G$: $\Func \xrightarrow{G}_+ r$, the remainder equals to
$$r = a_5i^2+a_6i+(a_7+a_8)ij_0+(a_9+a_{11}+a_{12})j_0^2+(a_{10}+a_{13})j_0+a_{14}$$
Let it equal to 0, then each coefficient will generate a constraint. The solution to the system forms the candidate
assignment to generate loop invariants.
\begin{equation}
\label{eqn:parasys}
\left\{
\begin{array}{l}
a_5=a_6=a_{14}=0\\
a_7+a_8=0\\
a_9+a_{11}+a_{12}=0\\
a_{10}+a_{13}=0
\end{array}\right.
\end{equation}

3) {\bf Modeling state transitions:}
A typical state transition starts from the previous state (PS) and ends at next state (NS). 
Our proposed approach models the 2 states individually,
{\it i.e.} performs polynomial reduction separately and obtains remainder $r_1$ and $r_2$. 
Assume a constraint polynomial describing
the state transition is $r_t$, then we require that when invariant of PS holds and transition $PS \to NS$ stands,
the invariant of NS should also be satisfied:
$$(r_1 = 0)\land (r_t = 0) \implies (r_2 = 0)$$
One reasonable conjecture is
$$r_t = r_1 - \lambda r_2$$
Theoretically $\lambda$ can be any polynomial in arbitrary rings. To make it practical, in terms of solving the system, 
we limit $\lambda$ to the polynomial ring with only real numbers.

Take Equation \ref{eqn:loopinv} as the example (which refers to Example 10 in \cite{sankaranarayanan2004non}). 
PS is initial state we just characterized 
$$\Func = f(s,i,j,j_0)$$ 
and NS has exactly the same form of constraint:
$$\Func' = f(s',i',j',j_0')$$
Considering the transition relation, we substitute $s'$ with $s+i$ and replace $j'$
with $j-1$, $i'$ for $i$, $j_0'$ for $j_0$, respectively. 
The template for NS is polynomial $f'$ in Example 10 in \cite{sankaranarayanan2004non}.

We then perform reduction with the Gr\"obner basis generated from the transition relation modeling, 
which is the Gr\"obner basis of polynomial ideal corresponding to the gates in the circuit partition.
After recording the NS remainder $r_2$,
by using equality $r_2 = \lambda r_1$ we get constraints for the parameters. We solve the system using 
similar algorithm to solve binate covering problems
which is also described in Section 4 as \emph{elimination by splitting} technique in \cite{sankaranarayanan2004non}. 
One of the branching results is:
\begin{align*}
&a_0,a_2,\dots, a_6, a_9,\dots,a_{14}=  0\\ 
&a_1=a_7=-a_8
\end{align*}
The reduced remainder is: 
$$r_2 = a_1s +(a_1-a_7)i+a_7ij+a_8ij_0 = a_1(s+ij-ij_0) = 0$$
Thus the invariant of the program in Equation \ref{eqn:loopinv} is:
$$s = i(j_0- j)$$
We can verify the invariant by executing the program which calculates $i\times j_0$. 
Initially $s=0$, $j_0-j=0$, invariant holds;
during each cycle, $s'=s+i, (j_0'-j') = (j_0-j)+1$, the invariant also holds. In conclusion, this is a
loop invariant for program in Equation \ref{eqn:loopinv}.

{\bf Our proposed approach on technology mapping:}
Our approach is inspired by the concept of templates in \cite{sankaranarayanan2004non}. 
However, we make an improvement on the original approach:
instead of using a template polynomial to describe the system, we add some extra templates into the ideal
of macro blocks which serve as technology mapping candidates. In this way we can cover all possibilities
of boundary cutting (circuit partition).

1) {\bf System abstraction:}
The polynomial we use to test ideal membership should include all the information of a circuit partition,
which requires us to abstract information from the system and write it into a single polynomial.
Usually this polynomial has the following generic form:
$$Z + f(i_1,i_2,\dots,i_n)$$
where $Z$ is the output. When there is only one output, $Z$ collapses to a bit-level variable. However in most
cases there are multiple outputs on the cut, indicating $Z$ as a word-level variable. Boolean function $\Func$ covers
all inputs, and $i_1,i_2,\dots,i_n$ are all bit-level inputs.

\begin{figure}[h]
	\begin{center}
	\includegraphics[width=\textwidth]{newfig/tobemapped.pdf}
	\end{center}
	\caption{An example gate-level netlist of a target sub-circuit to be mapped. ``$\blacksquare$" denotes a pin, 
	which is the boundary for the mapper.}
	\label{fig:tobemapped}
\end{figure}

Figure \ref{fig:tobemapped} shows an example circuit partition with $s_0,s_1,s_2,s_3$ as inputs and
$Z = \{z_0,z_1\}$ as outputs. If we use elements from Galois field $\F_{2^2}$ to represent word $Z$,
we have $Z = z_0 + \alpha\cdot z_1$.

After imposing ATO of LEX with
$$\textit{Other\ circuit\ variables} > \textit{output\ word\ } Z > \textit{all\ cut-set\ bit\ level\ inputs}$$
on the ideal describing the partitioned circuit as well as ideal with vanishing polynomials,
the reduced Gr\"obner basis has a single polynomial generator in the form of $Z + \Func(s_0,s_1,s_2,s_3)$.
In this example:

\begin{itemize}
\item Term ordering: $\{z_0,z_1,t,g_1,p_1,ci,t_1,t_2\}>Z>\{s_0,s_1,s_2,s_3\}$
\item Gate description: $z_0+t+g_1+t\cdot g_1, t+t_1+t_2+t_1\cdot t_2, g_1+s_0\cdot s_1,
			t_1+s_0\cdot ci, t_2+s_1\cdot ci, ci+s_2\cdot s_3, z_1+p_1+ci, p_1+s_0+s_1$
\item Word definition: $Z+z_0+z_1\cdot \alpha$
\item Vanishing polynomial ideal $(J_0)$: $z_0^2+z_0, z_1^2+z_1, t^2+t, g_1^2+g_1, t_1^2+t_1, t_2^2+t_2, p_1^2+p_1, ci^2+ci,
			s_2^2+s_2, s_3^2+s_3, s_0^2+s_0, s_1^2+s_1, Z^4+Z$ (since Z is a 2-bit word)
\end{itemize}

The result is a Gr\"obner basis with single polynomial generator. The polynomial has leading term $Z$:
$$Z+s_2\cdot s_3\cdot s_0+s_2\cdot s_3\cdot s_1+\alpha\cdot s_2\cdot s_3+s_0\cdot s_1+\alpha\cdot s_0+\alpha\cdot s_1$$

@@

2) {\bf Templates on Boundary Information:}
\begin{figure}[h]
	\begin{center}
	\includegraphics[width=\textwidth]{newfig/template.pdf}
	\end{center}
	\caption{Candidate cell: a standard 2-bit adder with one possible input/output mapping.}
	\label{fig:template}
\end{figure}

Figure \ref{fig:template} shows a 2-bit standard cell. It has 3 outputs ($t_0,t_1,CO$) mapped to 2 output pins ($z_0,z_1$),
and 4 inputs ($a_0,a_1,b_0,b_1$) mapped to 3 input pins ($s_0,s_1,s_2$, the excessive input {\it e.g.} $b_1$ is assigned to fixed 0/1 signal). Dashed connection
lines show one possible mapping, to find out this kind of feasible mapping, we need to simulate
all possible mappings, where the concept "template" can be used.

{\it Output template}: $z_0+c_{{t_0}{z_0}}\cdot t_0+c_{t_1z_0}\cdot t_1+c_{z_0CO}\cdot CO+c_{n_0}$

Above polynomial includes all possibilities where $z_0$ could be mapped to.
When $c_{n_0} = 0$, then $\{c_{t_0z_0},c_{t_1z_0},c_{z_0CO}\}$ equals to 1 denotes a valid mapping to corresponding output pin. 
Conversely if $c_{n_0} = 1$, the ``1" evaluation denotes mapping to negation of corresponding output pin.

{\it Input template}: $a_0+c_{s_0a_0}\cdot s_0+c_{s_1a_0}\cdot s_1+c_{s_2a_0}\cdot s_2+p_{a_0}$

When $p_{a_0} = 0$, then $\{c_{s_0a_0},c_{s_1a_0},c_{s_2a_0}\}$ equal to 1 denotes a valid mapping to corresponding input
pin. Conversely if every variable in set $\{c_{s_0a_0},c_{s_1a_0},c_{s_2a_0}\}$ equals to 0, 
it denotes mapping to fixed signal ``0" (when $p_{a_0} = 1$ then
mapping to fixed signal ``1").

With these settings, we propose an approach to perform technology mapping with boundary information:
\begin{itemize}
\item First, choose a cut-set of independent wires in target circuit as input pins;

\item Second, propagate forward the cut for a certain number of gates (depth), choose a cut-set
which fully dependents on these inputs as output pins. Thus we obtain a sub-circuit by partitioning;

\item Third, abstract a description polynomial $\Func$ of the target sub-circuit using GB based abstraction;

\item Fourth, reduce the description polynomial $\Func$ with the GB we computed associated to macro block 
and templates, obtain a remainder polynomial;

\item Last, but not the least, abstract all coefficients from the remainder polynomial and set up 
a system of equations similar to Equation \ref{eqn:parasys}.
If we find a solution to this system, then the solution is a feasible mapping; no solution means we cannot make a
feasible mapping.
\end{itemize}

### 2016-12-24 dissertation/submission/normal.tex
dissertation after defense update 2

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/Moore.eps}
\caption{A typical Moore machine and its state transition graph}
\label{fig:Moore}}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/convention.eps}
\caption{Conventional verification techniques based on bit-level unrolling and equivalence checking}
\label{fig:convention}}
\end{figure}

@@

\section{Formal Verification of Normal Basis Multipliers using Gr\"obner Bases}
The gate-level design of a NB multiplier can be generated using approaches introduced in 
Section \ref{sec:nbdesign}. The gate-level netlist is ready to be verified using 
an approach similar to that in Chapter \ref{ch:reacha}. 
First we introduce the sketch of our approach using abstraction term order (ATO)
mentioned previously in Section \ref{sec:abstraction}, then refine our approach using 
the concept of ``RATO", which is previously used in Section \ref{sec:improve}.
% The following part borrows contents
% from my own conference paper \cite{myDATE}.
\subsection{Implicit Unrolling based on Abstraction with ATO}
\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/comb_RAB.pdf}
\caption{Architecture of a combinational GF multiplier}
\label{fig:comb_RAB}}
\end{figure}

>>>>

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/Moore.eps}
\caption{A typical Moore machine and its state transition graph.}
\label{fig:Moore}}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/convention.eps}
\caption{Conventional verification techniques based on bit-level unrolling and equivalence checking.}
\label{fig:convention}}
\end{figure}

@@

\section{Formal Verification of Normal Basis Multipliers using Gr\"obner Bases}
The gate-level design of a NB multiplier can be generated using approaches introduced in 
Section \ref{sec:nbdesign}. The gate-level netlist is ready to be verified using 
an approach similar to that in Chapter \ref{ch:reacha}. 
First we introduce the sketch of our approach using abstraction term order (ATO)
mentioned previously in Section \ref{sec:abstraction}, then refine our approach using 
the concept of ``RATO", which is previously used in Section \ref{sec:improve}.
% The following part borrows contents
% from my own conference paper \cite{myDATE}.
\subsection{Implicit Unrolling based on Abstraction with ATO}
\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/comb_RAB.pdf}
\caption{Architecture of a combinational GF multiplier.}
\label{fig:comb_RAB}}
\end{figure}
